Syntax and Semantics of Indexed Abstract Binding Trees

### 2015-11-08 paper.tex
wordsmithing

In parallel, M.\ Fiore and his collaborators have developed the categorical
semantics for several variations of second-order algebraic theories
\cite{fiore:1999, fiore:2005, fiore-hur:2010, fiore-mamoud:2010}; of these, the
simply sorted second order algebraic theories treated by Fiore et al.\ are
equivalent to abstract binding trees augmented with a notion of second-order
variable (metavariable).

>>>>

In parallel, M.\ Fiore and his collaborators have developed the categorical
semantics for several variations of second-order algebraic theories
\cite{fiore:1999, fiore:2005, fiore-hur:2010, fiore-mamoud:2010}; of these, the
simply sorted variants are equivalent to Harper's abstract binding trees
augmented with a notion of second-order variable (metavariable).
